---
title: "Big Data Test"
author: "Sidney Hann"
date: \ `r params$date ` \
output:
  html_document:
    theme: cerulean
    highlight: tango
    toc: true
    number_sections: true
    fig.width: 7
params:
    date: !r format(Sys.time(), "%d %B, %Y")
---

Above is the YAML, using the `params` option to set the date.

## Global Settings

This next code chunk is visible in our RMarkdown document and within this code chunk the options for `knitr` will be set up. Since the option for the code chunk is `include=FALSE` this code chunk will not be printed in our final knitted report.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set Up Library

Using the `library` statement we can load the tidyverse. This will allow us to use pipes, `%>%` to subset our code and make it look cleaner. 

```{r load-libs, message=FALSE, warning=FALSE}
library(tidyverse)
```

## Load Data

This next code chunk will use a dataset, `Excitement`, to showcase the ability of RMarkdown to encorperate code, output, and Markdown to generate a easily readable, and reproducable report.

```{r load-data}
Excitement <- read.csv(file = "Excite.csv")
```

## Make a Plot of Satisfaction by Length of Presentation in Minutes With Code Showing

```{r Satisfaction-Plot}
Excitement %>% 
  ggplot(mapping = aes(x=Length_of_Presentation, y=Satisfaction_From_Presentation)) + #our aes statement will tell R which variables we would like on each axis
  geom_point() + #geom_point is used to make the scatterplot
  xlab("Length of Presentation in Minutes") +
  ylab("Satisfaction Level of the Audience (Satistfaction units)") + #xlab and ylab are used to make our axis more readable
  ggtitle("Plot of Satisfaction by Length of Presentation in Minutes")
```


## Make a Plot of Satisfaction by Length of Presentation in Minutes Without Code Showing (echo = FALSE)

```{r Satisfaction-Plot2, echo=FALSE}
Excitement %>% 
  ggplot(mapping = aes(x=Length_of_Presentation, y=Satisfaction_From_Presentation_Real)) + #our aes statement will tell R which variables we would like on each axis
  geom_point() + #geom_point is used to make the scatterplot
  xlab("Length of Presentation in Minutes") +
  ylab("Satisfaction Level of the Audience (Satistfaction units)") + #xlab and ylab are used to make our axis more readable
  ggtitle("Plot of Satisfaction by Length of Presentation in Minutes")
```


## Knitting

So now you have your RMarkdown code laid out. What to do now?

KNIT!

As Rachel mentioned, there are three ways to do this:

  1. Click the "Knit" button
  
  2. Press Ctrl+Shift+K
  
  3. With the code `rmarkdown::render("inputfile.Rmd")
  
  
```{r knit, echo=FALSE}
#rmarkdown::render("BigDataTest.Rmd")
```
